A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-12-11 doc/review-acom/response-to-referees.tex

The question of addressing this problem under weaker assumptions of smoothness of the boundary
is a very interesting one. To the best of our knowledge, this
question hasn't even been addressed for the eigenvalues of the Laplacian.
We have a sketch of a proof of convergence for the eigenvalues and eigenfunctions
for the Laplace operator where we can show that the eigenvalues and eigenfunctions
converge at an algebraic rate (dependent on the smoothness of curves) for $C^{\ell}$,
with $\ell\geq 2$, boundaries. The procedure of using the Fredholm determinant as
stated does not work on Lipchitz boundaries, since the corresponding operators are
not second kind.

However, we feel that the discussion would be fairly technical and distract
from the main results of the paper --- demonstrating the use of Fredholm determinants
and second kind formulations for computing the Stokes operator eigenvalues and
eigenfunctions.  For this reason we feel that this analysis should be carried out in
a separate work and done for both the Laplace and Stokes cases.

We've included a sketch of the proof below.

The main estimate needed is to show that the error in computing
the Fredholm determinant at an eigenvalue of the Stokes operator
is directly proportional to the quadrature error in 
evaluating the integral operator applied to the null vector (A proof sketch 
of this result for the Laplace case is contained in~\cref{sec:appb}. 
The red text in the appendix denotes results that need to be shown.). 
Based on the second-kind nature of the operator from $C^{m,\alpha} \to C^{m,\alpha}$
for $m<\ell$ and $\alpha>0$ (when the boundary is $C^{\ell}$) one can show
that the resulting null vector must be at least in $C^{m,\alpha}$.
The quadrature error using Kress quadratures converges algebraically
when both the boundary and density being approximated are $C^{m,\alpha}$.

### 2019-12-11 doc/draft-01-stokes/appendix-b.tex

\section{Sketch of proof}
\label{sec:appb}
Let $T_{n}$ denote the space of trigonometric polynomials
$\{ e^{-int}, \ldots e^{int} \}$. 
Let $\mathcal{K}$ denote the Helmholtz double layer integral operator
given by
\begin{equation}
\mathcal{K}[\phi] = \frac{i}{2}\int_{\Gamma} k H_{1}^{1}(k|x(t)-y(t)|) \frac{(x(t)-y(t))\cdot n(y(t))}{|x(t)-y(t)|} \phi(y(t)) dS_{y} \,
\end{equation}
where $k$ the Helmholtz parameter is assumed to be a dirichlet eigenvalue of the simply connected
domain $\Omega$ whose boundary is given by $\Gamma$, $(x(t),y(t)): [0,2\pi] \to \Gamma$ is
an arclength parameterization of the boundary, and $H_{1}^{1}$ is the Hankel function
of the first kind of order $1$.
It is well known that if $\Gamma$ is of class $C^{\ell,\alpha}$, then the
integral operator $\mathcal{K}: C^{\ell-1,\alpha} \to C^{\ell-1,\alpha}$ is a compact operator.
Furthermore, as shown in Zhao and Barnett, at the simple Dirichlet eigenvalues of the operator
$I + \mathcal{K}$ is not invertible and has a one dimensional null-space. Let $\phi_{0}$ denote
the null vector. 
By Fredholm theory, the adjoint $I + \mathcal{K}^{\ast}$ also has a one-dimensional null space.
Let $\psi_{0}$ denote the null vector of $I+\mathcal{K}^{\ast}$.

In order to prove the regularity of the eigenfunctions, we need to analyze
the kernels in $C^{\ell-1,\alpha}$ space. 
However in order to obtain a bound for the magnitude of the Fredholm
determinant, it is more convenient to work in $L^{2}$. It is well known
that the integral operator $I + \mathcal{K}$ is a second kind
Fredholm operator from $L^{2} \to L^{2}$ as well.
For the remainder of the section, we will work with $L^{2}$.

@@

And finally the operator $C_{n}$ is the restriction of $I_{n} + K_{n}$ as a map from
$P_{n} \phi_{0} \to P_{n} \psi_{0}^{\perp}$ and is given by
\begin{equation}
C_{n}P_{n} \phi_{0} = (I_{n} + K_{n}) P_{n} \phi_{0} - \left( (I_{n} + K_{n}) \phi_{0}, P_{n} \psi_{0} \right)P_{n} \psi_{0}
\end{equation}

@@

First, we observe that $D_{n}$ is the restriction of an operator in trace class
with a kernel whose leading order singularity is $r^{2} \log{r}$. 
{\color{red} Thus, $D_{n}$ is itself in trace class, and extending the proof of Bornemann to this case,
we observe that the discrete determinant of $D_{n}$ converges to the Fredholm determinant
of $D$ at a rate of at least $O(1/n)$. This in particular implies that
$\sup_{n} |\det{D_{n}}| <\infty$}.
Using Cauchy-Schwarz, we get that
\begin{equation}
\begin{aligned}
|A_{n}| &\leq |P_{n} \psi_{0}|_{2} |(I_{n} + K_{n})P_{n} \phi_{0}|_{2} \\
|B_{n}D_{n}^{-1} C_{n}| &\leq |B_{n}||D_{n}^{-1}|(1+ |P_{n} \psi_{0}|^2) |(I_{n} + K_{n})P_{n} \phi_{0}| \,.
\end{aligned}
\end{equation}
$B_{n}$ is a discretized block of a bounded operator and hence is bounded, 
and $D_{n}^{-1}$ is a bounded operator by the discussion above.

>>>>

\section{Sketch of proof}
\label{sec:appb}
Let $T_{n}$ denote the space of trigonometric polynomials
$\{ e^{-int}, \ldots e^{int} \}$. 
Let $\mathcal{K}$ denote the Helmholtz double layer integral operator
given by
\begin{equation}
\mathcal{K}[\phi] = \frac{i}{2}\int_{\Gamma} k H_{1}^{1}(k|x(t)-y(t)|) \frac{(x(t)-y(t))\cdot n(y(t))}{|x(t)-y(t)|} \phi(y(t)) dS_{y} \,
\end{equation}
where $k$ the Helmholtz parameter is assumed to be a dirichlet eigenvalue of the simply connected
domain $\Omega$ whose boundary is given by $\Gamma$, $(x(t),y(t)): [0,2\pi] \to \Gamma$ is
an arclength parameterization of the boundary, and $H_{1}^{1}$ is the Hankel function
of the first kind of order $1$.
It is well known that if $\Gamma$ is of class $C^{\ell,\alpha}$, then the
integral operator $\mathcal{K}: C^{\ell-1,\alpha} \to C^{\ell-1,\alpha}$ is a compact operator.
Furthermore, as shown in Zhao and Barnett, at the Dirichlet eigenvalues, the operator
$I + \mathcal{K}$ is not invertible and has a $p-$dimensional null-space, where
$p$ is the multiplicity of the eigenvalue. 
By Fredholm theory, the adjoint $I + \mathcal{K}^{\ast}$ also has a $p$-dimensional null space.
For convenience, we restrict our attention to the case $p=1$. This
part of the analysis extends to non-simple eigenvalues as well. 
Let $\phi_{0}$ denote
the null vector. 
Let $\psi_{0}$ denote the null vector of $I+\mathcal{K}^{\ast}$.

In order to prove the regularity of the eigenfunctions, we need to analyze
the problem in $C^{\ell-1,\alpha}$ space. 
However in order to obtain a bound for the magnitude of the Fredholm
determinant, it is more convenient to work in $L^{2}$. It is well known
that the integral operator $I + \mathcal{K}$ is a second kind
Fredholm operator from $L^{2} \to L^{2}$ as well.
For the remainder of the section, we will work with $L^{2}$.

@@

And finally the operator $C_{n}$ is the restriction of $I_{n} + K_{n}$ as a map from
$P_{n} \phi_{0} \to P_{n} \psi_{0}^{\perp}$ and is given by
\begin{equation}
C_{n}P_{n} \phi_{0} = (I_{n} + K_{n}) P_{n} \phi_{0} - \left( (I_{n} + K_{n}) P_{n}\phi_{0}, P_{n} \psi_{0} \right)P_{n} \psi_{0}
\end{equation}

@@

First, we observe that $D_{n}$ is the restriction of an operator in trace class
with a kernel whose leading order singularity is $r^{2} \log{r}$. 
{\color{red} Thus, $D_{n}$ is itself in trace class, and extending the proof of Bornemann to this case,
we observe that the discrete determinant of $D_{n}$ converges to the Fredholm determinant
of $D$ at a rate of at least $O(1/n)$. This in particular implies that
$\sup_{n} |\det{D_{n}}| <\infty$}.

Using Cauchy-Schwarz, we get that
\begin{equation}
\begin{aligned}
|A_{n}| &\leq |P_{n} \psi_{0}| |(I_{n} + K_{n})P_{n} \phi_{0}| \\
|B_{n}D_{n}^{-1} C_{n}| &\leq |B_{n}||D_{n}^{-1}|(1+ |P_{n} \psi_{0}|^2) |(I_{n} + K_{n})P_{n} \phi_{0}| \,.
\end{aligned}
\end{equation}
$B_{n}$ is a discretized block of a bounded operator and hence is bounded, 
and $D_{n}^{-1}$ is a bounded operator by the discussion above.
